# Data visualisation



```{r message= FALSE}
library(tidyverse)
```

## Introduction

> "The simple graph has brought more information to the data analyst's mind than any other device" -- John Tukey

This chapter teaches **data visualization** using ggplot2.

### Exercise 

No exercise.

## First steps

### Exercise


**Q1.** Run `ggplot(data = mpg)`. What do you see?

```{r ex3.2.4q1}
ggplot(data = mpg)
```

**Ans1.** A blank plot. We have not mapped anything to aesthetics.

**Q2.** How many rows in `mpg`? How many columns?

**Ans2.** Running `dim(mpg)` gives 234 rows and 11 columns. Alternatively one can also run `nrow(mpg)` to obtain number of rows and `ncol(mpg)` to obtain the columns. Futher, one can also use `str(mpg)`. The first line conatins the required information.

```{r ex3.2.4q2}
dim(mpg)
```

**Q3.** What does `drv` variable describe? Read the help for `?mpg` to find out.

**Ans3.** The `drv` describes how the cars drives *i.e.* by front two wheels, the rear wheels or all four wheels.

```{r echo = FALSE}
library("knitr")
drv <- data.frame("f" = "front-wheel drive", "r" = "rear wheel drive", "4" = "4wd")
names(drv) <- c("f","r","4")
kable(drv)
```

**Q4.** Make a scatter plot for `hwy` vs `cyl`.  
**Ans4.**

```{r ex3.3.4q4}
ggplot(mpg, mapping = aes( x = hwy, y = cyl)) + geom_point()
```

**Q5.** What happens if you make a scatterplot of `class` vs `drv`? Why is the plot not useful?  
**Ans5.**

```{r ex3.2.4q5}
ggplot(mpg, mapping = aes( x = class, y = drv)) + geom_point() 
```

The plot is not useful because of overploting. For example there are many cars of compact class but from the plot it seems as if there are only two cars. 

## Aesthetic mapping

An __aesthetic__ is a visual property of the objects in the plot. It include things like __the color, the shape, or the size__ of the points. We can convey the information about the data by mapping the aesthetics in the plot to the variables in the dataset. For example, colors of the points can be mapped to the `class` variable to show the class of each car. 

### Exercise

**Q1.** What's wrong with this code? Why are the points not blue?

```{r ex3.3.1q1}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

**Ans1.** In order for points to be colored the blue argumnet color should be outside the aes layer like shown below:

```{r ex3.3.1q1_1}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```


**Q2.** Which variable in `mpg` are categorical?Which are continuous?(Hint: type `?mpg` to read the documentation for the dataset). How can you see this information when you run `mpg`)?  
**Ans2.** We can use either `?mpg`and read from the help page or can run `str(mpg)` to find out about the type of variables in the `mpg` dataset.

```{r ex3.3.1q2}
str(mpg)
```

**Q3.** Map a continuous variable to `color`, `size` and `shape`. How do these aesthetics behave differently for categorical vs. continuous variables?  
**Ans3.** 

i. Mapping **color to continuous variable.**

When mapping a continuous variable to `color`,for example `cty` is mapped to color,  a color gradient is displayed to represent the values of the continuous variable. By defalut ggplot creates a color gradient from light blue to dark blue.

```{r ex3.3.1q3_1}
ggplot(mpg, aes(x = displ, y = cty, color = cty)) + geom_point()
```

ii. Mapping **size to continuous variable.**

```{r ex3.3.1q3_2}
ggplot(mpg, aes(x = displ, y = cty, size = cty)) + geom_point()
```

iii. Mapping **shape to continuous variable.**  

```{r ex3.3.1q3_3, error=TRUE, results='markup', fig.keep='none'}
ggplot(mpg, aes(x = displ, y = cty, shape = cty)) + geom_point()
```

Mapping a shape to continuous variable does not make sense. The continuous variable have a natural order but shapes have no natural order for example we cannot say a rectangle is greater or less than a triangle.

iv. Mapping color to a categorical variable

```{r ex3.3.1q3_4}
ggplot(mpg, aes(x = displ, y = cty, color = class)) + geom_point()
```

**Q4.** What happens if you map the same variable to multiple aesthetics?  
**Ans4.** It is possible to map the same variable to multiple aesthetics provided the mapping is allowed for the aesthetic. However, mapping the same variable adds redundant information and should be avoided. For example `drv` variable is mapped to the `color` and `shape` aesthetic in the plot below.

```{r ex3.3.1q4}
ggplot(mpg, aes(x = displ, y = hwy, color = drv, shape = drv)) + geom_point()
```

**Q5.** What does the `stroke` aesthetic do?What shapes does it work with?(Hint: use `?geom_point`)  
**Ans5.** The `stroke` aesthetic is used to change the border for shapes 21-25 which is given as property to `geom_points()`. The size and color of the border can be altered with the `stroke` and `color`. For example

```{r ex3.3.1q5}
ggplot(mpg, aes(x = displ, y = hwy)) + geom_point(shape = 21, fill = "yellow", size = 3, stroke = 3, color = "black")
```

**Q6.** What happens if you map an aesthetic to something other than the variable name, like `aes(color = displ <5)` ?  
**Ans6.** This will divide the data in two parts and create a temporary boolean variable indicating `TRUE` if the observations satisfy the condition `FALSE` otherwise. For example

```{r ex3.3.1q6}
ggplot(mpg, aes(x = displ, y = cty, color = displ<5 )) + geom_point()
```


## Common Problems

While creating plots using ggplot it is mandatory to put `+` at the end and not at the start of the statements. For example 

```{r ex3.4.1q1, results="hide", fig.keep='none'}
ggplot(data = mpg) +
geom_point(mapping = aes(x = drv, y = cyl))
```

### Exercise 

No exercise.

## Facets

**Facets** are used to split the plots based on variables particularly useful for categorical variables. `facet_warp` is used to split the plot using single variable and `facet_grid` is used to split the plot using a combination of variables.

### Exercise

**Q1.** What happens if you facet on a continuous variable?  
**Ans1.** The facet will convert the continuous variable into factors and we get as many plots as factors. For example  

```{r ex3.5.1q1}
ggplot(mpg, aes(x = displ, y = cty, color = drv)) + geom_point() + facet_wrap(~cyl)
```

**Q2.** What do the empty cells in plot with `facet_grid(drv ~ cyl)` mean?How do they relate to this plot?

**Ans2.**  
```{r ex3.5.1q2}
ggplot(mpg, aes(x = displ, y = cty)) + 
         geom_point() +
         facet_grid(drv ~ cyl)
```

The empty grids in the `facet_grid(drv ~ cyl)` represents the fact that there are no observations for a particular combination of `drv` and `cyl`. 

**Q3.** What plot does the following code make? What does `.` do ?

**Ans3.** The general formula in the `facet_grid` plots  is `facet_grid(ROWS ~ COLUMNS)`. A `.` means to ignore the faceting in that dimension.

```{r ex3.5.1q3_1, results="hide"}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)
```

The first plot compares `displ` vs `hwy` and rows are facetted by `drv` while there is no facetting by columns.


```{r ex3.5.1q3_2, results="hide"}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

The second plot compares `displ` vs `hwy` and columns are facetted by `cyl` while there is no facetting by rows.

**Q4.** Take the first faceted plot in this section:

```{r ex3.5.1q4_1}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

**Ans4.** The advantage of faceting is clear when there are many groups in a large dataset. As the number of unique groups rise it becomes increasingly confusing to distinguish groups using different colors in the same plot. 

The same plot when the `class` is represented by color aesthetic rather than faceting.

```{r ex3.5.1q4_2}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, col = class))
```

A possible disadvantage of faceting is that since the observations are divided into separate plots a direct comparision may be difficult. Therefore, it may be worth showing each group with a different color in the same plot if the dataset is smaller and there are small numbet of groups to compare.

**Q5.** Read `?facet_wrap`. What does `nrow` do? What does `ncol` do? What other options control the layout of the individual panels? Why doesn't `facet_grid()` have `nrow` and `ncol` arguments?

**Ans5.** `nrow` and `ncol` refer to number of rows and columns of the panel in a `facet_wrap` plot. It is useful to specify number of rows or columns because `facet_wrap` facets using only one variable. For example  

*Facet with 1 row*  

```{r ex3.5.1q5_1}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 1)
```

*Facet with two rows*

```{r ex3.5.1q5_2}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

These arguments are unnecessary in `facet_grid` because the number of rows and columns are automatically calculated from the unique values of the variables specified in the `facet_grid(ROWS ~ COLUMNS)` command.

**Q6.** When using `facet_grid()` you should usually put the variable with more unique levels in the columns. Why?

**Ans6.** It is advised to put variables with more unique levels in columns in a landscape mode because it is much easier visually to see the trend in a dependent variable y by scanning horizontally. For example

*More unique levels in rows*

```{r ex3.5.1q6_1}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(class ~ drv)
```

*More unique values in columns*

```{r ex3.5.1q6_2}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ class)
```

## Geometric object

A **geom** is the geometric object that a plot uses to display the data. For example a line chart uses line geoms and bar chart uses a bar geoms and so on to display the data.

### Exercise

**Q1.** What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?

**Ans1.** 

- line chart: `geom_line()`
- boxplot:    `geom_boxplot()`
- histogram:  `geom_hist()`
- area chart: `geom_area()`

**Q2.** Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

```{r ex3.6.1q2_1, results='hide', fig.keep='none'}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

The above code will produce a scatterplot between `displ` and `hwy`. The points will be colored by `drv` and there will be a smooth line without standard errors for each group of `drv`. It is worth noticing that the mapping is defined in `ggplot()` therefore, it passes to `geom_point()` and `geom_smooth()`. 

```{r ex3.6.1q2_2, results='hide'}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

**Q3.** What does `show.legend = FALSE` do? What happens if you remove it? Why do you think I used it earlier in the chapter?

**Ans3.** `show.legend = FALSE` will hide the legend. For example

```{r ex3.6.1q3_1 }
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point(show.legend = FALSE)
```

If we remove it the legend is displayed which is automatically created when a variable is mapped to aesthetics like `size`, `shape` or `color`. The last part of the question refers to the following code

```{r ex3.6.1q3_2, results='hide', fig.keep='none'}
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy))
              
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv))

ggplot(data = mpg) +
  geom_smooth(
    mapping = aes(x = displ, y = hwy, colour = drv),
    show.legend = FALSE)
```

In the above code legend was suppressed in the last plot because the context of the code was to show the difference between mapping a variable to `group` (which does not add legend by itself) and `color` (which add legends) aesthetic. 

**Q4.** What does the `se` argument to `geom_smooth` do?

**Ans4.** `se` argument is used to display `se = TRUE` or hide `se = FALSE` the standard error bands to the line. `se` is `TRUE` by default. For example

`se = TRUE`

```{r ex3.6.1q4_1}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, colour = drv)) +
  geom_point() +
  geom_smooth(se = TRUE)
```

`se = FALSE`

```{r ex3.6.1q4_2}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, colour = drv)) +
  geom_point() +
  geom_smooth(se = FALSE)
```

**Q5.** Will these two graphs look different? Why/why not?

```{r ex3.6.1q5_1, results='hide', fig.keep='none'}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```

**Ans5.** No, because in the second plot both `geom_point()` and `geom_smooth()` take same data and mappings as defined in `ggplot` in the first plot. Infact geom objects can inherit those values from `ggplot` object, therefore, it is unnecessary to be specified again.

**Q6.** Recreate the R code necessary to generate the following graphs.

**Ans6.**

*Plot 1*

```{r ex3.6.1q6_1, message=FALSE}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

*Plot 2*

```{r ex3.6.1q6_2, message=FALSE}
ggplot(mpg, aes(x = displ, y = hwy, group = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

*Plot 3*

```{r ex3.6.1q6_3, message=FALSE}
ggplot(mpg, aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

*Plot 4*

```{r ex3.6.1q6_4, message=FALSE}
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = drv)) +
  geom_smooth(se = FALSE)
```

*Plot 5*

```{r ex3.6.1q6_5, message=FALSE}
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = drv)) + 
  geom_smooth(se = FALSE, aes(linetype = drv))
```

*Plot 6*

```{r ex3.6.1q6_6, message=FALSE}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point(color = "white", size = 4) + 
  geom_point(aes(color = drv))
```

## Statistical transformations

Some graphs like bar charts, boxplots uses an algorithim to calculate new values to generate a plot. The algorithim used is called **stat** (statistical transformations). For example bar charts, histograms or frequency polygons bin the data and then plot the count of the points that fall in each bin. The counts are originally not necessarily present in the original data.

### Exercise

**Q1.** What is the default geom associated with `stat_summary()`?. How could you rewrite the previous plot to use that geom function instead of the stat function?

**Ans1.** The default geom assocaited with `stat_summary` is `geom_pointrange`. See `?stat_summary`. The default stat in `geom_pointrange` is "identity" therefore, using "summary" and change the min, max and midpoint to produce the same plot.

```{r ex3.7.1q1_1}
ggplot(diamonds, aes(x = cut, y = depth)) + 
  geom_pointrange(stat = "summary",
                  fun.ymin = min, 
                  fun.ymax = max, 
                  fun.y = median
                  )
```

**Q2.** What does `geom_col()` do? How it is different to `geom_bar()`?

**Ans2.** The `geom_col()` and `geom_bar()` are used to make bar charts. The difference being `geom_col()` uses `stat_identity` as the default stat whereas `geom_bar()` uses `stat_count` as the default stat. In other words `geom_col()` expects that the data is preprocessed into x and y values and plots the data as it is whereas `geom_bar()` will create either of two variables(count or prop) and then plots the count data on the y axis.

**Q3.** Most geoms and stats come in pairs that are almost always used in concert. Read through the documentation and make a list of all the pairs. What do they have in common?

**Ans3.** Please look at the [documentation](http://ggplot2.tidyverse.org/reference/)

**Q4.** What variables does `stat_smooth()` compute? What parameters control its behaviour?

**Ans4.** The function `stat_smooth()` calculates the following statistics:
* y - predicted value
* ymin - lower value of the confidence interval
* ymax - upper value of the confidence interval 
* se - standard error

Based on `?stat_smooth` the statistics can be controlled with the method argument. There can be different methods like `lm`, `glm`, `loess` among others which determines the type of method used to calculate the predictions and confidence interval. 

**Q5.** In our proportion bar chart, we need to set `group = 1`. Why? In other words what is the problem with these two graphs?

```{r ex3.7.1q5, results='hide'}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop..))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = color, y = ..prop..))
```

**Ans5.** If the group is not set to 1, then all the bars have proportion == 1. By default `geom_bar()` treats number of x values as individual group and `stat` computes the count within each group therefore, we get prop == 1 for each value of x in the above graphs. 

Following is the version we mostly likely intended 

```{r ex3.7.1q5_1}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop.., group  = 1))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = color, y = ..prop.., group = color))
```

## Position adjustments
 The stacking is performed using the `position` argument. For no stacking use position = `"idendity"`, `"dodge"` or `"fill"`. postion = `"jitter"` adds small amount of random noise and is useful for scatter plots in avoiding **overploting**. 

### Exercise

**Q1.** What is the problem with this plot? How could you improve it?

```{r ex3.8.1q1, results='hide'}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()
```

**Ans1.** Overplotting is the problem. This can be improved using `position="jitter"` argument or `geom_jitter()`

```{r ex3.8.1q1_1}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point(postion = "jitter")
```

OR

```{r ex3.8.1q1_2}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter()
```

**Q2.** What parameters to `geom_jitter()` control the amount of jittering?

**Ans2.** There are two parameters that control the amount of jitter
* `width` - horizontal displacement
* `height` - vertical displacement

**Plot with no jitter**

```{r ex3.8.1q2_1}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()
```

**Plot with `width = 0`, no horizontal displacement**

```{r ex3.8.1q2_2}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
geom_jitter(width = 0, height = 1)
```

**Plot with `height = 0`, no vertical displacement**

```{r ex3.8.1q2_3}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
geom_jitter(width = 1, height = 0)
```

**Plot with horizontal and vertical displacement**

```{r ex3.8.1q2_4}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
geom_jitter(width = 1, height = 1)
```

**Q3.** Compare and contrast `geom_jitter()` with `geom_count()`.

**Ans3.** 
`geom_jitter()` adds the random noise in the plot. It reduces the overplotting however, at the cost of altering the actual `x` and `y` values of the points. For example:

```{r ex3.8.1q3_1}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_jitter()
```

`geom_count()` controls the size the points based on the frequency of observations at each location. In other words points with more observations will be larger than with fewer observations. This does not change the actual `x`  and `y` values however, is prone to overplotting if the points are large and close to each other.For example:

```{r ex3.8.1q3_2}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_count()
```

**Q4.** What’s the default position adjustment for `geom_boxplot()`? Create a visualizaion of the `mpg` dataset that demonstrates it.

**Ans4.** As per the documentation the default position for `geom_boxplot()` is `"dodge"`. 

```{r ex3.8.1q4_1}
ggplot(data = mpg, mapping = aes(x = drv, y = cty, colour = manufacturer)) +
  geom_boxplot()
```

## Coordinate systems

### Exercise

**Q1.** Turn a stacked bar chart into a pie chart using `coord_polar()`.

**Ans1.** Stacked bar chart

```{r ex3.9.1q1_1}
ggplot(data = mpg, mapping = aes(x = factor(1), fill = class)) + 
  geom_bar()
```

and the corresponding pie chart is shown below. Please see [documentation](https://ggplot2.tidyverse.org/reference/coord_polar.html) for explanation of the argument `theta`.

```{r ex3.9.1q1_2}
ggplot(data = mpg, mapping = aes(x = factor(1), fill = class)) + 
  geom_bar(width = 1) + 
  coord_polar(theta = "y")
```

**Q2.** What does `labs()` do? Read the documentation. 

**Ans2.** It is used for modifying labels and plot legends. For example:

```{r ex3.9.1q2_1}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty )) + geom_boxplot() + coord_flip() + labs(y = "City MPG", x = "", title = "City MPG by manufacturer")
```

**Q3.** What is the difference between `coord_quickmap()` and `coord_map()`?

**Ans3.** From the [documentation](https://ggplot2.tidyverse.org/reference/coord_map.html) of `coord_map` it is `coord_quickmap` is a quick approximation of the `coord_map` algorithim to project a portion of earth, which is spherical, onto a flat 2D plane using a projection called "mercator" defined in `mapproj` package.

```{r ex3.9.1q3_1}
library("maps")
nz <- map_data("nz")
nzmap <- ggplot(nz, mapping = aes(x = long, y = lat, group = group)) +
  geom_polygon(color = "black", fill = "white")

nzmap + coord_map()
nzmap + coord_quickmap()
```

**Q4.** What does the plot below tell you about the relationship between city and highway mpg? Why is `coord_fixed()` important? What does `geom_abline()` do?

```{r ex3.9.1q4}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```

**Ans4.** The plot tells us that `hwy` mpg is always higher than city mpg and there is a strong positive correlation. `coord_fixed` is important because 
> A fixed scale coordinate system forces a specified ratio between the physical representation of data units on the axes. -- Documentation of coord_fixed()

The default `ratio = 1`. Ratio greater than 1 make unit on the y axis longer than the units on the x axis. For example:

* ratio > 1

```{r ex3.9.1q4_1}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() + 
  coord_fixed(ratio = 2)
```

* ratio < 1

```{r ex3.9.1q4_2}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed(ratio = 0.5)
```

Finally `geom_abline()` adds reference lines also called rules to the plot either horizontal, vertical or diagonal(using `slope` and `intercept` arguments). The default values are `slope=1` and `intercept=0`. If any point fall on reference line it indicates that highway and city mpg are same for that point. For example both the codes produce the same plot:

```{r ex3.9.1q4_3}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed() + 
  expand_limits(x = 0, y = 0)
```

```{r ex3.9.1q4_4}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() + 
  expand_limits(x = 0, y = 0)
```

## The layered grammer of graphics

> The grammer of graphics is based on the insight that you can uniquely describe *any* plot as a combination of dataset, a geom, a set of mappings, a stat, a position adjustments, a coordinate system and a faceting scheme. -- R for Data Science

### Exercise

No exercise.
