# Workflow:basics

```{r, message=FALSE}
library("tidyverse")
```

## Coding basics

R can be used as a calculator.

### Exercise 

No exercise. 

## What's in the name

i_am_snake_case

IAmCamelCase

i.am.period.case

i_am.MixCase

### Exercise

No exercise.

## Calling functions

Call functions using the syntax below:

`function_name(arg1 = value1, arg2 = value2)`

### Exercise 

No exercise.

## Practice

### Exercise

**Q1.** Why does the code does not work?

```{r ex4.4.1q1, error=TRUE, collapse=TRUE}
my_variable <- 10
my_varıable
```

**Ans1.** The code does not work because the variable which is assigned the value 10 is `my_variable` whereas the variable being called is different. The R will throw an error if it cannot find the variable in the environment.

**Q2.** Tweak each of the following R commands so that they run correctly:

```{r ex4.4.1q2, error=TRUE, collapse=TRUE,fig.keep='none'}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
filter(diamond, carat > 3)
```

**Ans2.** There are typos in the above code. Although, the first part of the code is correct.
```{r ex4.4.1q2_1}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
```

`fliter` should be `filter` and `=` should be `==`

```{r ex4.4.1q2_2}
filter(mpg, cyl == 8)
```

diamond should be diamonds

```{r ex4.4.1q_3}
filter(diamonds, carat > 3)
```

**Q3.** Press Alt + Shift + K. What happens? How can you get to the same place using the menus?

**Ans3.** It gives the keyboard shortcuts menu. The same can be achieved under Tools -> Keyboard shortcuts or Help -> Keyboard shortcuts.